```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(cluster)
library(reshape2)
library(GGally)
library(readxl)
library(ggpubr)

###Import Data Set
undf <- read.csv("melbourne_housing.csv")
df <- read.csv("melbourne_housing.csv")
head(df, 10)
glimpse(df)

nrow(df) ### = 13580 Prices of Houses Pre-omitting NA
ncol(df) ### = Number of Variables before Cleaning
```

```{r}
df %>% summarize_all(n_distinct)
```

```{r}

###Data Cleaning - Removing Nonessential Variables that do not predict price

df <- df %>% select(-c(Address, Suburb, Method, Postcode, Bedroom2, SellerG, Propertycount)) %>% na.omit()
head(df, 10)

nrow(df) ### = 6830 House Post-omitting NA
```

```{r}

###Reformatting Variables 

df$YearSold <- as.numeric(format(as.Date(df$Date, format="%d/%m/%Y"),"%Y"))
df$MonthsSince2016 <- (as.numeric(format(as.Date(df$Date, format="%d/%m/%Y"),"%Y"))-2016)*12 + as.numeric(format(as.Date(df$Date, format="%d/%m/%Y"),"%m"))
df <- df %>% mutate(BuildingAge=YearSold-YearBuilt)
df <- df %>% filter(BuildingAge >= 0) %>% select(-YearBuilt, -Date)
df <- df %>% select(Price,Regionname, CouncilArea, MonthsSince2016, BuildingAge, Landsize, BuildingArea, Lattitude, Longtitude, Type, Rooms, Distance, Bathroom, Car)
```
```{r}

###Converting Character Variables Into Integers

RegionName <- as.factor(df$Regionname)
RegionName <- unclass(RegionName)
df$Regionname <- RegionName

CouncilArea <- as.factor(df$CouncilArea)
CouncilArea <- unclass(CouncilArea)
df$CouncilArea <- CouncilArea

Type <- as.factor(df$Type)
Type <- unclass(Type)
df$Type <- Type

```

```{r}
###Exporting Final Cleaned DataSet

write.csv(df, "final_cleaned_df.csv")
```

```{r}

###Converting Integers to Numeric

df$Price <- as.numeric(df$Price)
df$CouncilArea <- as.numeric((df$CouncilArea))
df$MonthsSince2016 <- as.numeric((df$MonthsSince2016))
df$Landsize <- as.numeric((df$Landsize))
df$Type <- as.numeric((df$Type))
df$Rooms <- as.numeric((df$Rooms))
df$Bathroom <- as.numeric((df$Bathroom))
df$Car <- as.numeric((df$Car))
df$Regionname <- as.numeric((df$Regionname))

###Correlationmatrix
no_categorical_df <- df %>% select(Price, MonthsSince2016, BuildingAge, Landsize, BuildingArea, Lattitude, Longtitude, Rooms, Distance, Bathroom, Car)

correlationmatrix_df = round(cor(no_categorical_df), 2)
head(correlationmatrix_df)
```

```{r}
get_lower_tri <- function(correlationmatrix_df) {
    correlationmatrix_df[upper.tri(correlationmatrix_df)] <- NA
    return(correlationmatrix_df)
}

lower_tri = get_lower_tri(correlationmatrix_df)
lower_tri
```

```{r}
meltedcorrelationmatrix_df <- melt(lower_tri, na.rm = TRUE)
head(meltedcorrelationmatrix_df)
```

```{r}

###Correlation Heat Map

dfheatmap = ggplot(data = meltedcorrelationmatrix_df,
    aes(Var2, Var1, fill = value)) + geom_tile(color = "white") +
    scale_fill_gradient2(low = "blue", high = "red",
        mid = "white", space = "Lab", name = "Correlation") +
    theme(axis.text.x = element_text(angle = 45, vjust = 1,
        size = 9, hjust = 1)) + coord_fixed() + geom_text(aes(Var2,
    Var1, label = value), color = "black", size = 2)

dfheatmap
```

```{r}

###Clustering

wss <- vector()

for (i in 1:10) {
    temp <- df %>%
        kmeans(i)
    wss[i] <- temp$tot.withinss
}

ggplot() + geom_point(aes(x = 1:10, y = wss)) + geom_path(aes(x = 1:10,
    y = wss)) + xlab("clusters") + scale_x_continuous(breaks = 1:10)
```

```{r}
kmean = no_categorical_df %>%
    kmeans(3)
kmeansclust <- no_categorical_df %>%
    mutate(cluster = as.factor(kmean$cluster))

df_pam = pam(no_categorical_df, 3)
head(df_pam)
```

```{r}
df_pam$silinfo$avg.width
```

```{r}

###Can Someone make this look pretty?
newdf = no_categorical_df %>%
    mutate(cluster = as.factor(df_pam$clustering))

ggpairs(newdf, aes(color = cluster))
```


```{R}
p2 <- ggplot(df, aes(x=Landsize, y=Price))
p2 + geom_point(aes(color=Price)) + geom_smooth(method=lm) + stat_cor(method = "pearson")
```


```{R}
p3 <- ggplot(df, aes(x=BuildingArea, y=Price))
p3 + geom_point(aes(color=Price)) + geom_smooth(method=lm) + stat_cor(method = "pearson")
```


```{R}
p3 <- ggplot(df, aes(x=Distance, y=Price))
p3 + geom_point(aes(color=Price)) + geom_smooth(method=lm) + stat_cor(method = "pearson")
```


```{R}
undf_Regionname <- undf %>% filter(Regionname=="Eastern Victoria" | Regionname=="Northern Metropolitan" | Regionname=="Northern Victoria" | Regionname=="South-Eastern Metropolitan" | Regionname=="Western Metropolitan") 
p4 <- ggplot(undf_Regionname, aes(x=Landsize, y=Price, color=Regionname))
p4 + geom_point() + geom_smooth(method=lm) + stat_cor(method = "pearson") + ylim(0, 4500000)
```


```{R}
p5 <- ggplot(undf_Regionname, aes(x=BuildingArea, y=Price))
p5 + geom_point(aes(color=Price)) + geom_smooth(method=lm) + stat_cor(method = "pearson")
```


```{R}
undf_Pvalue <- undf %>% filter(Regionname=="Eastern Metropolitan" | Regionname=="Northern Metropolitan" | Regionname=="South-Eastern Metropolitan" | Regionname=="Western Metropolitan" | Regionname=="Eastern Victoria" | Regionname=="Northern Victoria") 
p6 <- ggplot(undf_Pvalue, aes(x=Distance, y=Price, color=Regionname))
p6 + geom_point() + geom_smooth(method=lm) + stat_cor(method = "pearson") + facet_grid(rows=vars(Regionname)) + scale_y_continuous(limits = c(0, 2500000))
```
**We observe that the Distance from CBD (Commercial Business District) to the property has little-to-none effect on the price of that property in Eastern and Northern Victoria. In general, CBD represent the prosperity of a city, so the price should go up as the property gets closer to the CBD; however, this is not the case in the Victoria district. Might be because the CBD of Victoria sucks.**

```{R}
p7 <- ggplot(undf_Regionname, aes(x=Propertycount, y=Price, color=Regionname))
p7 + geom_point() + geom_smooth(method=lm) + stat_cor(method = "pearson") + facet_grid(rows=vars(Regionname)) + scale_y_continuous(limits = c(0, 2500000))
```

swiss = swiss
